\documentclass[12pt]{article}
\usepackage[a4paper, total={19cm,27cm}]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{float}
\usepackage{multicol}
\setlength{\columnsep}{-9cm}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\pagestyle{empty}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{multirow}
\graphicspath{ {./images/} }
\usepackage{mathspec}
\usepackage{xeCJK}
\setmainfont{Sabon LT Pro} 
\setsansfont{SF Pro Text}
\renewcommand{\baselinestretch}{0.9}
\titleformat*{\section}{\Large \bfseries}
\titleformat*{\subsection}{\sffamily}
\titleformat*{\subsubsection}{\bfseries}

\begin{document}
\begin{multicols}{2}
    \section*{Po-Sheng Cheng}
    \href{https://bencer3283.github.io/art/}{\underline{Online Portfolio Link}}
    
    \columnbreak
    {\sffamily \small \noindent
    Master of Industrial Design, Rhode Island School of Design, Jun. 2026 \newline
    B.Sc. Bio-Mechatronics Engineering \& \newline B.A Economics, National Taiwan University (NTU), Jan 2023
    }
\end{multicols}
{\small \noindent Innovative prototype engineer with 5 years of diverse experience in cutting-edge product development.}
\subsection*{Core Competencies}
{ \small \begin{itemize}
    \item Electrical: Arduino, ESP32, Raspberry Pi, system interfaces (I2C, SPI) and PCB design
    \item Mechanical: CAD (SolidWorks, Fusion, Pro/E Creo), rapid prototyping (CNC, FDM/STL 3D Printing)
    \item Programming: C++, Java, Node.js (Express, React), Dart (Flutter), Python (PyTorch, NumPy), git
    \item Design: Rhino, Keyshot, Figma wireframing, Adobe Suite
\end{itemize}}
    \section*{Professional Experience}
    \subsection*{Graduate Instructor, RISD Co-Works Lab, Sep. 2024 -  \hfill Providence, RI}
    
    \subsection*{Apprentice, Google Hardware Product Sprint, Jun. - Sep. 2024\hfill Taipei, Taiwan}
        { \small
        \begin{itemize}
            \item Spearheaded development of an innovative HaaS lost and found platform, incorporating advanced kiosk technology and intuitive software service
        \end{itemize}
        }
    \subsection*{E-Lab Research Assistant, RISD Industrial Design, Feb. 2024 -  \hfill Providence, RI}
        { \small
        \begin{itemize}
            \item Led comprehensive workshops on electronics, Arduino/ESP32, RESTful API, web backend, and mobile app development
            \item Efficiently managed and optimized E-Lab component inventory
        \end{itemize}
        }
    \subsection*{(Publication) TeleSHift: Telexisting TUI for Physical Collaboration \& Interaction}
    { \small
    {\scriptsize Andrew Chen, Tzu-Ling Yang, Shu-Yan Cheng, \textbf{Po-Sheng Cheng}, Tzu-Han Lin, and Kaiyuan Lin. 2022. Recipient of the \textbf{Best Demo Award at Ubicomp/ISWC 2022 Conference}, https://doi.org/10.1145/3544793.3560323}
        \begin{itemize}
            \item Engineered an innovative shape-transforming device with advanced 3D tangible user interface, revolutionizing group collaboration
            \item Architected comprehensive system infrastructure, integrating mechanical design and power supply circuits
            \item Pioneered design for manufacturability improvements, slashing assembly time by 80\%
        \end{itemize}
        }
    
        \subsection*{Electro-mechanical Engineering Intern, Logitech, Feb. - Jun. 2022\hfill Hsinchu, Taiwan}
        { \small
        \begin{itemize}
            \item Conducted in-depth user research, interviewing 50 students to drive innovation in gaming keyboard design
            \item Engineered sophisticated Arduino-based control system for precision motor and electromagnet operation
            \item Gained comprehensive understanding of New Product Introduction (NPI) process, fostering cross-departmental collaboration across ID, PM and EE
        \end{itemize}
        }
        \subsection*{College Student Researcher, NTU, Jul. 2021 - Feb. 2022\hfill Taipei, Taiwan}
        { \small
        \begin{itemize}
            \item Pioneered development of cutting-edge spectral mapping system, integrating EMCCD with LabVIEW/C++
            \item Optimized core algorithm, achieving a 26\% reduction in scanning time
            \item Honored with the 2021 Technology Innovation Award and College Student Research Creativity Award
        \end{itemize}}
        \subsection*{Project Lead, Bio-Electromagnetics Laboratory, NTU, May. 2020 - Jul. 2022\hfill Taipei, Taiwan}
        { \small
        \begin{itemize}
            \item Conceptualized and implemented advanced IoT system for precision monitoring of agricultural pests
            \item Established efficient git-based SolidWorks collaboration workflow and Notion-based BOM management system
            \item Leveraged expertise in automation, IoT (Arduino, XBee), PCB design (Altium), SolidWorks, and MySQL to deliver comprehensive solution
        \end{itemize}
        }
        
\end{document}